### 2014-05-08 BUGS/long_observation_period.Rmd
add md files from /inst/examples on master branch

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 70  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <- K # observations start from
x0 <- Xo # simulation under policy starts from
Tobs <- 20
```

>>>>

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 20  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <- K # observations start from
x0 <- Xo # simulation under policy starts from
Tobs <- 70
```

### 2014-05-08 BUGS/myers.Rmd
add md files from /inst/examples on master branch

```{r myers-mcmc, dependson="myers-model"}
```

>>>>

```{r myers-mcmc-local, dependson="myers-model"}
jags.params=c("r0", "theta", "K", "stdQ")
jags.inits <- function(){
  list("r0"= 1.5 * rlnorm(1,0,.2), 
       "K"=    8 * rlnorm(1,0,.1),
       "theta" = 2.5 * rlnorm(1,0,.1),  
       "stdQ"= sqrt(0.2) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags.parallel, 
                      list(data=jags.data, inits=jags.inits, 
    											 jags.params, n.chains=n.chains, 
													 n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, 
                           model.file="myers_process.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=n.update, 
                           n.iter=n.iter, n.thin = n.thin, 
                           progress.bar="none"))
```

### 2014-05-08 admb-example.Rmd
add md files from /inst/examples on master branch

```{r stateeq}
f <- function(x,h,p)  x * exp(p[1] * (1 - x / p[2]) * (x - p[3]) / p[2] ) 
p <- c(1, 10, 5)
K <- 10  # approx, a li'l' less
allee <- 5 # approx, a li'l' less
```

@@

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
z_g <- function() rlnorm(1,0, sigma_g)
x_grid <- seq(0, 1.5 * K, length=50)
Xo <-  allee + 0.5 # observations start from
Tobs <- 40
set.seed(123)
```

@@

```{r obs, dependson="sdp-pars"}
x <- numeric(Tobs)
x[1] <- Xo
for(t in 1:(Tobs-1))
  x[t+1] = z_g() * f(x[t], h=0, p=p)

```

@@

```{r mle, dependson="obs"}
n = length(x)
loglik <- function(p){ 
  r = p[1]; k = p[2]; c = p[3]; s = p[4];
  mu = x + r * (1 - x / k) * (x - c) / k;
  0.5 * n * log(2 * pi) + n * log(s) + 0.5 * sum(x - mu)^2/ s^2;
  #-sum(dlnorm(x, mu, s), log=TRUE) # above equation is equivalent to results from built-in function
  }
init <- c(1, 1, 1, 1)
o <- optim(init, loglik, method="L", lower=1e-5, upper=100)
o$par
```

@@

PROCEDURE_SECTION
  mu = x + r * elem_prod((1 - x / k), (x - c) / k);
  f = 0.5 * n * log(2 * M_PI) + n * log(s) + 0.5 * norm2(x - mu) / square(s);
")
writeLines(model, "model.tpl")
```

```{r run-admb}
setup_admb("/var/admb")

df <- data.frame(x=x)
params <- list(r = 1, k = 10, c = 2, s = .1) ## starting parameters
bounds <- list(r = c(1e-5, 100), k=c(1e-5, 100), c=c(1e-5, 100), s = c(1e-5,100)) ## bounds
dat <- c(list(n = nrow(df)), df)
m1 <- do_admb("model",
              data = dat,
              params = params,
              bounds = bounds,
              run.opts = run.control(checkparam="write",
                                     checkdata="write", clean=FALSE))
m1
```

Which now matches the results from `optim`, now that we avoid the k=0 bound.

>>>>

```{r stateeq}
f <- function(x,h,p)  x * exp(p[1] * (1 - x / p[2]) * (x - p[3]) / p[2] ) 
p <- c(1, 10, 5)
K <- 10  # approx, a li'l' less
Xo <- 6 # approx, a li'l' less
```

@@

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.1
z_g <- function() rlnorm(1,0, sigma_g)
x_grid <- seq(0, 1.5 * K, length=50)
Tobs <- 40
set.seed(123)
```

@@

```{r obs, dependson="sdp-pars"}
x <- numeric(Tobs)
x[1] <- Xo
for(t in 1:(Tobs-1))
  x[t+1] = z_g() * f(x[t], h=0, p=p)
qplot(1:Tobs, x)
```

@@

```{r mle, dependson="obs"}
STABLIZE = 1e-10
n = length(x)
mloglik <- function(pars){ 
  r = pars[1]; k = pars[2]; c = pars[3]; s = pars[4];
  mu = (x+STABLIZE) * exp( r * (1 - x / (k+STABLIZE)) * (x - c) / (k + STABLIZE));
  mu = pmin(1e100, mu) # avoid infinite values 
  f = 0.5 * n * log(2 * pi) + n * log(s + STABLIZE) + 0.5 * sum(x - mu + STABLIZE)^2/ (s + STABLIZE)^2;

  f
  }
```

Starting from the true values we mostly just shrink the noise parameter:

```{r}
init <- c(p, sigma_g)
mloglik(init) #true minus loglik
o <- optim(init, mloglik, method="L", lower=1e-5, upper=1e5)
o$value
o$par
```

While starting from arbitrary values we still find the optim.

```{r}
init <- c(1,1,1,1)  
init <- c(p, sigma_g)
mloglik(init) #true minus loglik
o <- optim(init, mloglik, method="L", lower=1e-5, upper=1e5)
o$value
o$par
```

@@

PROCEDURE_SECTION
  mu = log(x) + r * elem_prod((1 - x / k), (x - c) / k);
  f = 0.5 * n * log(2 * M_PI) + n * log(s) + 0.5 * norm2(x - exp(mu)) / square(s);
")
writeLines(model, "model.tpl")
```

Without explicit handling of the overflow errors, ADMB does not give us reliable estimates with arbitrary starting conditions

```{r run-admb1}
setup_admb("/var/admb")

df <- data.frame(x=x)
params <- list(r = 1, k = 1, c = 1, s = 1) ## starting parameters
bounds <- list(r = c(1e-10, 1e3), k=c(1e-10, 1e3), c=c(1e-10, 1e3), s = c(1e-5,1e3)) ## bounds
dat <- c(list(n = nrow(df)), df)
m1 <- do_admb("model",
              data = dat,
              params = params,
              bounds = bounds,
              run.opts = run.control(checkparam="write",
                                     checkdata="write", clean=FALSE))
m1
```

But does fine with good starting values.  Hmm.. thought that was supposed to be the other way around...

```{r run-admb}
params <- list(r = 1, k = 10, c = 5, s = .1) ## starting parameters

m1 <- do_admb("model",
              data = dat,
              params = params,
              bounds = bounds,
              run.opts = run.control(checkparam="write",
                                     checkdata="write"))
m1
```

Which finds a better optim (though substantailly overfit in reality)

### 2014-05-08 allee.Rmd
add md files from /inst/examples on master branch

```{r}
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=TRUE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
```

>>>>

```{r}
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(10,1600,2),
          m0r1=FALSE, corr="exp", trace=TRUE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
```

### 2014-05-08 myer-example.Rmd
add md files from /inst/examples on master branch

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

>>>>

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/", warning=FALSE)
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

```{r gp-priors}
```

### 2014-05-08 tgp-priors.Rmd
add md files from /inst/examples on master branch

```{r include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE, message=FALSE)
theme_update(plot.background = element_rect(fill = "transparent",colour = NA))
```

>>>>

```{r include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE, message=FALSE)
```
